Rigid fluid coupling

### 2022-05-23 manuscript/paper.tex
Add controlled sliding case. Automated many examples.

\begin{abstract}
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
\begin{itemize}
\item Rigid bodies in fluid flows in nature. Where can we find them? What kind
  of problems do they give rise to? Ice-Sea? Debris?
\item Many different ways RFC is been modeled, this includes mesh based and
  mess less. Explain in a good detail what meshless methods are out there
  which handles these problems. This includes SPH too.
\item Explain SPH history and its applications in different areas. Now SPH
  specifically applied in RFC area. Detail some papers where how differently
  fluid is modelled, this includes ISPH, WCSPH, TVF, delta+ SPH. Also mention
  the latest multiphase flow, where air is considered, then mention the
  adaptive formulation, where the author captures the cavity.
\item Similarly explain the many ways the rigid-rigid coupling is been
  handled. Detail how non-smooth boundaries are handled.
\item Mention the open source software which provide SPH formulation (there are 2.)
\item Explain what we are going to do in the current work. We adapt the
  Mohseni formulation to handle the non-smooth boundaries, we also incorporate
  the damping, and extend the formulation to 3d and simulate 3d problems.
\item Explain the examples. 3d Sliding case, 3d controlled sliding case, body
  falling in water, then 3d dam break over dynamics rigid obstacles.
\end{itemize}

@@

@@

\subsection{3D Bouncing cube on a wall under gravity}
\label{sec:bouncing-cube}

@@

In the current section we test the frictional part of the current solver by
modeling the sliding of a rigid body on an inclined surface in 3D. We compare
against the analytical solution to validate the test case.

@@

\Cref{fig:mohseni-2021-sliding-3d} shows the snapshots of the rigid body at 4
time instants. From \cref{fig:mohseni-2021-sliding-3d} we can see that the the
body is freely sliding with out having any oscillations or unphysical jumping
off the inclined wall. This is because of the new surface aware contact model
as force is not computed by considering the wall as spherical particles but by
ensemble of an overlap. The snapshots correspond to a friction coefficient of $0.4$.

@@

\Cref{fig:results-solid-sliding-velocity-vs-time} shows a evolution of
velocity of the center of mass of the rigid body for different frictional
coefficients against the analytical solution. From
\Cref{fig:results-solid-sliding-velocity-vs-time} we can see that the current
solver has an excellent match with the analytical solution and covers all the
regimes of the sliding case.

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Velocity versus time}
\label{fig:results-solid-sliding-velocity-vs-time}
\end{figure}

@@

@@

\Cref{fig:velocity-vs-time-controlled-sliding} depicts the time histories of
velocity of the center of mass of the rigid body with time, as well as the
variation of applied external normal $F_n$ and tangential $F_t$ forces.
\begin{itemize}
\item How the normal force is varied?
\item When does the tangential force come into picture?
\item What physics is supposed to follow?
\item Say that the current velocity variation is matching with the analytical one.
\end{itemize}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Velocity vs time of the rigid slider}
\label{fig:velocity-vs-time-controlled-sliding}
\end{figure}

@@

@@

\begin{figure}[!htpb]
  \centering
  % \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Schematic of the controlled rigid body sliding}
\label{fig:schematic-controlled-rigid-body-sliding}
\end{figure}

@@

\FloatBarrier%
\subsection{Floating solid in water}
\label{sec:floating-solid-in-water}

>>>>

\begin{abstract}
  In this paper, a new particle-based fluid–rigid-body interaction schemes are
  utilised to model violent free-surface flow problems. A variant of Discrete
  element method (DEM), surface aware DEM (SADEM) is proposed to handle the
  contact between irregular bodies, while the fluid phase is modeled using
  corrected transport velocity formulation (CTVF) of smoothed particle
  hydrodynamics (SPH). The accuracy the SADEM-CTVF framework are evaluated via
  several numerical examples involving both analytical and experimental.
  Surface aware DEM is validated using using numerical examples including: (1)
  A free and controlled sliding of a cube, (2) A 2d rolling disc. Further, an
  experimental benchmark, collapse of a stack of cylinders in a dam under
  gravity is considered, three rigid bodies hitting. While the coupling method
  is validated by modeling (1) water-entry of a sphere, (2) 3d dam breaking
  flow hitting stacked cubes. The results indicate that the current method can
  effectively model irregular bodies in a fluid flow.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
\begin{itemize}
\item Rigid bodies in fluid flows in nature. Where can we find them? What kind
  of problems do they give rise to? Ice-Sea? Debris?
\item Why is it hard to model rigid fluid coupling? Then we say numerically
  nonlinear, and this is how it is been into handled. Many different ways RFC
  is been modeled, this includes mesh based and messless. Explain in a good
  detail what meshless methods are out there which handles these problems.
  This includes SPH too. (Same as next point)
\item \todoin{Done} Describe some works where Rigid fluid coupling is handled
  in meshless methods. MPS-DEM, SPH-DEM and other ways, recently Asai. (Same
  as previous point)
\item Explain SPH history and its applications in different areas. Now SPH
  specifically applied in RFC area. Detail some papers where how differently
  fluid is modelled, this includes ISPH, WCSPH, TVF, delta+ SPH. Also mention
  the latest multiphase flow, where air is considered, then mention the
  adaptive formulation, where the author captures the cavity.
\item \todoin{Done} Similarly explain the many ways the rigid-rigid coupling is been
  handled. Detail how non-smooth boundaries are handled.
\item \todoin{Done} Explain what we are going to do in the current work. We adapt the
  Mohseni formulation to handle the non-smooth boundaries, we also incorporate
  the damping, and extend the formulation to 3d and simulate 3d problems.
\item Explain the examples. 3d Sliding case, 3d controlled sliding case, body
  falling in water, then 3d dam break over dynamics rigid obstacles.
% \item Mention the open source software which provide SPH formulation (there are 2.)
\end{itemize}

\textbf{Random points to be included later}.
\begin{itemize}
\item In the context of modeling the rigid fluid coupling by assuming both of
  them as particles and, these are the few papers. The more relevant concern
  the generalization of the fundamental technique of Koshizuka et al. [6] and
  the inclusion of a state-of-the-art Distributed Contact DEM (DCDEM)
  formulation, similar in concept to those employed by both Zhang et al. [14]
  and Ren et al. [15]. A delta -SPH [16] term is added to the continuity equation,
  controlling the density field fluctuations and contributing for the
  mitigation of known solid–fluid interface deficiencies [17], particularly
  the development of a hydrophobic area that results in a reorganization of
  the fluid particle positions.The current work
\item A one way coupling is done by xxxx. Then an semi empirical model is used
  to find the force on the discrete elements by stokes law or other laws. Then
  a two way coupling is introduced by Zhang, also Monaghan did the same
  approach.
\end{itemize}

\textbf{1st bullet point of introduction}. Irregular bodies are modeled using
many different variations now, one of the methods is by overlapped sphere
method \cite{das2007modeling}, SMR-DEM by \citet{zhan2021surface}, dilated
polyhedral DEM \citet{liu2020new}, Fourier series-based discrete element
method \citet{lai2020fourier}, non-smooth wall modeling by
\citet{amaro2019improvement}, GJK-DEM, DFR-DEM. In the current work we have
extended the contact force model proposed by \citet{mohseni2021particle} to
handle three dimensional problems, we also incorporate the damping model.

\textbf{5th bullet point of introduction}. Irregular bodies are modeled using
many different variations now, one of the methods is by overlapped sphere
method \cite{das2007modeling}, SMR-DEM by \citet{zhan2021surface}, dilated
polyhedral DEM \citet{liu2020new}, Fourier series-based discrete element
method \citet{lai2020fourier}, non-smooth wall modeling by
\citet{amaro2019improvement}, GJK-DEM, DFR-DEM. In the current work we have
extended the contact force model proposed by \citet{mohseni2021particle} to
handle three dimensional problems, we also incorporate the damping model.

\textbf{6th bullet point of introduction}. Numerical examples, collision of
three cubes is initially used to test the conservation property of the current
contact mode while dealing with non-smooth boundaries. Further, a free and
forced sliding of a 3d cube on a frictional inclined plane, and a rolling
cylinder whose analytical solutions exists are utilised to validate the
rigid-rigid contact model frictional model. A granular collapse of a stack of
cylinders is modeled and compared against the experimental results. In order
to validate the two-way rigid fluid coupled scheme a rigid circular body
falling in a steady tank is simulated. Complex interactions of fluid in a 3D
dam breaking with multiple rigid bodies, is studied and compared with the
experimental results of SPH-DCDEM.

@@

% check \cite{natsui2018sph}

@@

% \subsection{3D Bouncing cube on a wall under gravity}
% \label{sec:bouncing-cube}

@@

\begin{itemize}
\item Give details of gravity in schematic
\end{itemize}

In the current section we model free sliding of rigid cube on an inclined
frictional plane. The frictional part of the current solver by is validated
through this test. We consider both 2d and 3d case. The velocity of the center
of mass of the cube is compared against the analytical solution for
quantitative validation. The schematic is shown is figure

@@

\subsubsection{2D sliding}
\label{sec:results-2d-sliding}

\Cref{fig:mohseni-2021-sliding-2d} shows the snapshots of the rigid body at
three time instants. From \cref{fig:mohseni-2021-sliding-2d} we can see that
the the body is freely sliding with out having any oscillations or unphysical
jumping off the inclined wall. This is because of the new surface aware
contact model as force is not computed by considering the wall as spherical
particles but by ensemble of an overlap. The snapshots correspond to a
friction coefficient of $0.2$.
\Cref{fig:results-solid-sliding-velocity-vs-time-2d} shows a evolution of
velocity of the center of mass of the rigid body for different frictional
coefficients against the analytical solution. From
\Cref{fig:results-solid-sliding-velocity-vs-time-2d} we can see that the current
solver has an excellent match with the analytical solution and covers all the
regimes of the sliding case.

\begin{figure}[!htpb]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_2d/fric_coeff_0_2/time0}
    \subcaption{t = $0$ s}\label{fig:passing-0}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_2d/fric_coeff_0_2/time1}
    \subcaption{t = $0.5$ s}\label{fig:passing-1}
  \end{subfigure}

  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_2d/fric_coeff_0_2/time2}
    \subcaption{t = $1$ s}\label{fig:passing-2}
  \end{subfigure}
  \caption{Rigid body with friction $0.2$ sliding.}
\label{fig:mohseni-2021-sliding-2d}
\end{figure}

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_2d/velocity_vs_time}
  \caption{Velocity versus time}
\label{fig:results-solid-sliding-velocity-vs-time-2d}
\end{figure}

\subsubsection{3D sliding}
\label{sec:results-3d-sliding}

\Cref{fig:mohseni-2021-sliding-3d} shows the snapshots of the rigid body at 4
time instants. From \cref{fig:mohseni-2021-sliding-3d} we can see that the the
body is freely sliding with out having any oscillations or unphysical jumping
off the inclined wall. This is because of the new surface aware contact model
as force is not computed by considering the wall as spherical particles but by
ensemble of an overlap. The snapshots correspond to a friction coefficient of
$0.4$. \Cref{fig:results-solid-sliding-velocity-vs-time-3d} shows a evolution of
velocity of the center of mass of the rigid body for different frictional
coefficients against the analytical solution. From
\Cref{fig:results-solid-sliding-velocity-vs-time-3d} we can see that the current
solver has an excellent match with the analytical solution and covers all the
regimes of the sliding case.
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.6\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Velocity versus time}
\label{fig:results-solid-sliding-velocity-vs-time-3d}
\end{figure}

@@

@@

\begin{itemize}
\item How the normal force is varied?
\item When does the tangential force come into picture?
\item What physics is supposed to follow?
\item Say that the current velocity variation is matching with the analytical one.
\end{itemize}

@@

\Cref{fig:velocity-vs-time-controlled-sliding} depicts the time histories of
velocity of the center of mass of the rigid body with time, as well as the
variation of applied external normal $F_n$ and tangential $F_t$ forces.
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.7\textwidth]{figures/mohseni_2021_controlled_sliding_on_a_flat_surface_2d/case_1/force_velocity_vs_t}
  \caption{Velocity vs time of the rigid slider}
\label{fig:velocity-vs-time-controlled-sliding}
\end{figure}

@@

\todoin{Status: Done (Except add the particle plots)}

A cylinder of diameter $1.0$ m is allowed to roll on an inclined plane under
gravity. The physical model is shown in \cref{fig:circular-body:schematic-1},
while the computational model is in \cref{fig:circular-body:schematic-2}. In
the computational model the $x$-axis points in the direction of the slope,
while the gravity makes an angle $\theta$ with the vertical. The material
properties and the numerical parameters are given in
\cref{tab:circular-body-rolling-params}. A total of two friction coefficients
are simulated for, and for the quantitative validation center of mass of the
cylinder is considered, whose analytical expression is given as
\begin{align}
  \label{eq:analytical-x-cm-rolling-cylinder}
  x_{cm}(t) =
  \begin{cases}
  x_0 + \frac{1}{2} \, g \, t^2 \, (\sin(\theta) - \mu \cos(\theta)) & \tan{\theta} > 3.5\mu,\\
  x_0 + \frac{1}{3} \, g \, t^2 \, \sin(\theta) & \tan{\theta} \leq 3.5\mu.
\end{cases}
\end{align}
\begin{figure}[!htpb]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{images/de_2021_cylinder_rolling_on_an_inclined_plane/schematic_1}
    \subcaption{}\label{fig:circular-body:schematic-1}
  \end{subfigure}
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{images/de_2021_cylinder_rolling_on_an_inclined_plane/schematic_2}
    \subcaption{}\label{fig:circular-body:schematic-2}
  \end{subfigure}
  \caption{Curved interface}
\label{fig:circular-body-schematic}
\end{figure}
\begin{table}[!ht]
  \centering
  \begin{tabular}[!ht]{ll}
    \toprule
    Quantity & Values\\
    \midrule
    $\rho$, density & $2700$ kg\,m\textsuperscript{-3} \\
    $\mu$, friction coefficient & $0.3$ \& $0.6$ \\
    Time of simulation & $0.6$ s \\
    Resolution, $\delta x$ & $0.0025$ m\\
    Smoothing length factor, $h/\Delta x$ & 1\\
    gravity $[g_x, g_y, g_z]$ & $[g\,\sin(\theta), g\,\cos(\theta), 0.0]$\\
    $k_r$, Repulsive stiffness coefficient & $1e7$ \\
    $k_f$, Repulsive stiffness coefficient & $1e5$ \\
    $\alpha_{damp}$ & FIXME\\
    \bottomrule
  \end{tabular}
  \caption{Material properties and numerical parameters used for the rolling
    of cylinder on an inclined surface.}%
  \label{tab:circular-body-rolling-params}
\end{table}

\Cref{fig:cylinder-xcom-vs-time-fric-0-3} and
\cref{fig:cylinder-xcom-vs-time-fric-0-3} depicts the variation of center of
mass of the cylinder with time for a friction coefficients of $0.3$ and $0.6$.
From both the figures we can see that the center of mass predicted by the
current solver is at an excellent agreement with the exact solution. Further
\todo{put the right figure} \cref{fig:cylinder-xcom-vs-time-fric-0-3} shows
the snapshots of the cylinder at different time stamps, from which we can see
that the current scheme is stable.

@@

\begin{figure}[!htpb]
  \centering
  % \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Schematic of the three rigid body colliding}
\label{fig:schematic-three-rigid-bodies-colliding}
\end{figure}

@@
